\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.

### 2015-07-17 paper/paper 2/dc-2015.tex
introduction

In this paper, we build on the experience gained from mapping several constraint languages to SPIN and from the analysis of the identified constraint types to create an intermediate layer, a framework that is able to describe the mechanics of all constraint types and that can be used to map high-level languages more easily.

>>>>

In this paper, we build on the experience gained from mapping several constraint languages to SPIN and from the analysis of the identified constraint types \tb{was haben wir analysiert? meinst du die constraint type specific expressivity of constraint languages?}to create an intermediate layer, a framework that is able to describe the mechanics of all constraint types and that can be used to map high-level languages more easily. \tb{sollten wir hier nicht alle contributions nennen? ich denke im abstact stehen sie alle}
